### 2023-08-24 documents/floats/ppekverbs.tex
missing references, last traces of _

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{sa} \rc{w-} in \PPek]{Verbs preserving \gl{1}\gl{sa} \rc{w-} in \PPek \parencites[153, 200]{alves2017arara}[42, 80, 139, 209]{ikpengpacheco2001}[129, 170]{meiraDBebakairi / pinto2022bakairi}[68]{ikpengpacheco1997}[4]{meira2003bakairi}[111]{pinto2022bakairi}{meiraDBebakairi}}
\label{tab:ppekverbs}
\begin{tabular}[t]{@{}lllll@{}}
\mytoprule
{} &          \PPek &          \arara &                       \ikpeng &                   \ebakairi \\
\mymidrule
\qu{say}     &    \rc{wɨ-ge-} &    \obj{wɨ-ge-} &                   \obj{ɨ-ge-} &  \obj{u-gue-} / \obj{u-ge-} \\
\qu{bathe}   &    \rc{w-ipɨ-} &    \obj{w-ibɨ-} &     \obj{{\normalfont ∅}-ip-} &                  \obj{w-i-} \\
\qu{be-1}    &     \rc{w-ap-} &     \obj{w-ap-} &                             – &                \obj{w-awɨ-} \\
\qu{be-2}    &  \rc{w-et͡ʃi-} &  \obj{w-it͡ʃi-} &  \obj{{\normalfont ∅}-et͡ʃi-} &                  \obj{w-i-} \\
\qu{come}    &    \rc{w-epɨ-} &    \obj{w-ebɨ-} &                 \obj{k-arep-} &               \obj{k-əewɨ-} \\
\qu{go down} &   \rc{w-ɨptə-} &                 &                               &                             \\
\qu{go}      &   \rc{w-ɨdən-} &    \obj{w-ɨdo-} &                 \obj{k-aran-} &                 \obj{u-də-} \\
\mybottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Verbs preserving \gl{1}\gl{sa} \rc{w-} in \PPek]{Verbs preserving \gl{1}\gl{sa} \rc{w-} in \PPek \parencites[153, 200]{alves2017arara}[42, 80, 139, 209]{ikpengpacheco2001}{meiraDBebakairi}[111, 129, 170]{pinto2022bakairi}[68]{ikpengpacheco1997}[4]{meira2003bakairi}}
\label{tab:ppekverbs}
\begin{tabular}[t]{@{}lllll@{}}
\mytoprule
{} &          \PPek &          \arara &                       \ikpeng &                   \ebakairi \\
\mymidrule
\qu{say}     &    \rc{wɨ-ge-} &    \obj{wɨ-ge-} &                   \obj{ɨ-ge-} &  \obj{u-gue-} / \obj{u-ge-} \\
\qu{bathe}   &    \rc{w-ipɨ-} &    \obj{w-ibɨ-} &     \obj{{\normalfont ∅}-ip-} &                  \obj{w-i-} \\
\qu{be-1}    &     \rc{w-ap-} &     \obj{w-ap-} &                             – &                \obj{w-awɨ-} \\
\qu{be-2}    &  \rc{w-et͡ʃi-} &  \obj{w-it͡ʃi-} &  \obj{{\normalfont ∅}-et͡ʃi-} &                  \obj{w-i-} \\
\qu{come}    &    \rc{w-epɨ-} &    \obj{w-ebɨ-} &                 \obj{k-arep-} &               \obj{k-əewɨ-} \\
\qu{go down} &   \rc{w-ɨptə-} &                 &                               &                             \\
\qu{go}      &   \rc{w-ɨdən-} &    \obj{w-ɨdo-} &                 \obj{k-aran-} &                 \obj{u-də-} \\
\mybottomrule
\end{tabular}
\end{table}

### 2023-08-24 documents/sections/extensions.tex
missing references, last traces of _

All descriptions of \ikpeng list \obj{k-} as the only \gl{1}\gl{sa} marker \parencites[55]{ikpengpacheco1997}[105]{campetela1997analise}[64]{ikpengpacheco2001}[205]{alves2013verbo}.
However, most \ikpeng cognates of the verbs in question do not take \obj{k-}, but rather \obj{ɨ-} or Ø \exref{ikpw}, with the exception of \obj{k-}prefixed \qu{to go} \exref{ikp-170}.
While reflexes of \rc{a[p]} \qu{be-1} do exist in \ikpeng, apparently only reflexes of \rc{eti} \qu{be-2} occur with first person prefixes \parencite[401]{gildea2018reconstructing}.

>>>>

All descriptions of \ikpeng list \obj{k-} as the only \gl{1}\gl{sa} marker \parencites[55]{ikpengpacheco1997}[105]{campetela1997analise}[64]{ikpengpacheco2001}[205]{chagas2013verbo}.
However, most \ikpeng cognates of the verbs in question do not take \obj{k-}, but rather \obj{ɨ-} or Ø \exref{ikpw}, with the exception of \obj{k-}prefixed \qu{to go} \exref{ikp-170}.
While reflexes of \rc{a[p]} \qu{be-1} do exist in \ikpeng, apparently only reflexes of \rc{eti} \qu{be-2} occur with first person prefixes \parencite[401]{gildea2018reconstructing}.
